A formal approach but practical approach in train regulation

### 2025-06-19 paper/main.tex
Début Section dynamique

%% tt style
\newcommand{\sigred}{{\mbox{${\color{red!50!black}\mathtt{r}}$}}\xspace}
\newcommand{\siggreen}{{\mbox{${\color{green!50!black}\mathtt{g}}$}}\xspace}

\newcommand{\deviate}{{\mbox{$\mathtt{v}$}}\xspace}
\newcommand{\direct}{{\mbox{$\mathtt{d}$}}\xspace}

@@

At each end of the blocks, there is a signal whose state is \sigred (red) or \siggreen (green). In other words, the status of signals is described by a function $F: \blocks \times \directions \to \{ \sigred, \siggreen\}$. Given some signal status $F$, a block $\posFmt{pos}$ and a direction $dir$, $F(pos,dir) = \sigred$ means the signal guarding the exit of block $\posFmt{pos}$ in direction $\dirFmt{dir}$ is red, and we expect trains not leaving that block going in this direction\footnote{Our semantics, presented below, ensure such behaviour.}\todo{ref}. The signal status is entirely determined by the network configuration and the locking status due to the regulator\todo{Le régulateur n'est pas encore introduit, je propose de déplacer ça plus bas.}.

@@

\section{Modèle formel}
\label{sec:formal-model}

Description par des règles. La gestion du temps est "discrétisée". On ne peut pas "choisir" quelle est la bonne règle. Gestion par des gardes, et des messages. Il y a des soucis grand pas, petit pas. Dire comment on gère les évt, comment on régule l'application des règles.

>>>>

%% Signals
\newcommand{\sigred}{{\mbox{${\color{red!50!black}\mathtt{r}}$}}\xspace}
\newcommand{\siggreen}{{\mbox{${\color{green!50!black}\mathtt{g}}$}}\xspace}
\newcommand{\deviate}{{\mbox{$\mathtt{v}$}}\xspace}
\newcommand{\direct}{{\mbox{$\mathtt{d}$}}\xspace}
\newcommand{\signalF}[2]{\ensuremath{F(\posFmt{#1}, \dirFmt{#2})}}

%% Reduction relation
\newcommand{\reduces}{\ensuremath{\rightarrow}}

%% tt style

@@

At each end of the blocks, there is a signal whose state is \sigred (red) or \siggreen (green). In other words, the status of signals is described by a function $F: \blocks \times \directions \to \{ \sigred, \siggreen\}$. Given some signal status $F$, a block $\posFmt{pos}$ and a direction $\dirFmt{dir}$, $\signalF{pos}{dir} = \sigred$ means the signal guarding the exit of block $\posFmt{pos}$ in direction $\dirFmt{dir}$ is red, and we expect trains not leaving that block going in this direction\footnote{Our semantics, presented in Section~\ref{sec:formal-model}, ensure such behaviour.}. The signal status is entirely determined by the network configuration and the locking status due to the regulator\todo{Le régulateur n'est pas encore introduit, je propose de déplacer ça plus bas.}.

@@

\section{Model Semantics/Model dynamics}
\label{sec:formal-model}

In the previous section, we introduced our model. In this section, we present the dynamics of our model, that is the rules that govern how our model can switch from one state to the other. The dynamics is described by means of a reduction relation, characterising the successive states of our model. We define this reduction relation using inference rules, described hereafter.

\todo{Expliquer le temps discret et le mix grand pas/petit pas.}
